Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-18 fib2.tex
show braiding and observables

>>>>

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-syndrome.pdf}
\caption{Four equivalent representations of a state,
along with two syndrome observables marked with solid and dashed lines:
(a) two pairs are joined in (b).
Deform the curve straight to get (c),
then effect some
braid operations on the state so that (d) the two
observables are now represented on the curve.
}
\label{f:syndrome}
\end{center}
\end{figure}
